---
title: "Election_Project"
author: "Sky Liu, Longhao Chen, Emma Zhang"
date: "10/15/2018"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
require(gdata)
```


#Table DonorList1: Key is contributor ID, which is a unique ID corresponding each individual donated in the election. The attributors are donor name, city, states, organization, date, amount, recipient ID
```{r}
DonorList = read.xls ("Donations to MA Cands 2018.xlsx", sheet = 1, header = TRUE)
DonorList1 <- dplyr::select(DonorList,contribid,contrib,City,State,orgname,date,amount,recipid)
```


#Table StateList: Key is the state. Attributes are the number of donors and total amount of donation
```{r}
StateList <- DonorList1 %>% 
  group_by(State) %>% 
  summarise(
    n = n(),
    TotalDonation = sum(amount)
  )
```

#Table RecipientList: The key is Candidate who receives donation from recipients. The attributes are cities/States the candidates are from, the amount of donation they recived, date, and the desription of expenditure.

```{r}
MA <- read.xls("MA_Candidate_Expenditures.xlsx")
Expr<-dplyr::select(MA,c(Candidate,City,Amount,Date,State,Description))
View(Expr)
Expr1<-ta
Expr1<- na.omit(Expr)
sort(Expr$Amount)
```